---
title: "survey_results_Aug2023"
author: "Geraldine Klarenberg, PhD"
format: html
editor: visual
---

# Using collaborative open science tools to improve engagement with the ecology of the Guana River Estuary

### August 2023

#### *Geraldine Klarenberg, Kristie Perez, Nikki Dix, Nia Morales, and Shirley Baker*

The University of Florida and Guana Tolomato Matanzas National Estuarine Research Reserve (GTMNERR) are partnering with the local community and broader science community to develop a web-based, public-facing, interactive dashboard to provide access to Guana River Estuary (GRE) datasets. The aim of this work is to support open science and to increase diverse engagement with GRE within the GTMNERR by making the data available interactively, using visualization tools.

To this end, the project team sought feedback from those who have been involved with the GTMNERR to help them to better understand their needs. This document summarizes the results of an online survey that was made available via email, social media, and QR code.

```{r, load_package_data, echo = FALSE, message = FALSE}
library(tidyverse)
library(kableExtra)
intro <- read_csv("data_deidentified/subsets/intro_results_basic.csv")
demogr <- read_csv("data_deidentified/subsets/demographics_results_basic.csv")
```

## Previous experiences with accessing data

## Those that have access data

## Those that have not accessed data

## Dashboard preferences

## Characteristics of respondents

```{r age, fig.width = 4, fig.height = 3, echo = FALSE}
ggplot(demogr %>% 
         filter(qname == "DE-2"),
       aes(y = fct_rev(factor(q_text))))+
  geom_bar(fill = "seagreen3") +
  scale_x_continuous(breaks = function(x) seq(0, floor(x[2]), by = 2))+
  labs(x = "", y = "", title = "What is your age group?") +
  theme_bw()
```

```{r gender, fig.width = 4, fig.height = 3, echo = FALSE}
DE3 <- demogr %>% 
  filter(qname == "DE-3") %>% 
  group_by(q_text) %>% 
  summarize(cnt = n()) %>%
  mutate(percentage = round(cnt/sum(cnt)*100, 1)) 

DE3 %>% kable(col.names = c("What is your gender?", "Count", "Percentage")) %>% 
  kable_paper(bootstrap_options = "striped", full_width = FALSE)

ggplot(DE3,
       aes(x = factor(q_text), y = percentage, fill = factor(q_text)))+
  geom_col() +
  labs(x = "", y = "Percentage", title = "What is your gender?") +
  scale_fill_manual(values = c("purple", "darkgreen"))+
  theme_bw()+
  theme(legend.position = "none")
```

## Trust

Decide if to keep in
